---
title: "Modelfitting"
author: "Simon&Andrea"
date: '2022-10-120'
output: html_document
---

```{r setup, include=FALSE}
pacman::p_load(tidyverse, rjson, DEoptim, doParallel, here,data.table,jsonlite,lme4,nnet,brms)
knitr::opts_knit$set(root.dir = here()) # set root fot the whole file
refit=T
```

In this document, we will fit learning model to the "social bandit" task that Andrea and I developed. 
First, lets load some data.

```{r}

## load behavioral data
social_data <-  read_csv(file = paste0("./data/social/data_social_all_participants.csv")) %>%#drop_na()
  filter(tot_points>0 & !is.na(demo_type))%>%#filter(player<30)%>%# get a sub-sample of both adults and adolescents 
  mutate(soctype=case_when(
    demo_type=="gem_found"~1,# i need that to index the different social weight parameters
    demo_type=="gem_not_found"~2,
    demo_type=="never_exploit"~3,
    demo_type=="no_gem"~4)
  )
```

# Fit model to social data
This function fits the model specified in models_mle and stores the parameter estimates as well as the fit index (lower is better)
alongside the participant data in long format. In the future we want to modify this to fit different models.

There is a credible interaction between SI use and agegroup
```{r}
social_data%>%group_by(demo_type,player,round,group)%>%
  count(social_info_use)%>%filter(!is.na(social_info_use))%>%filter(social_info_use=="copy")%>%
  ggplot(aes(x=round,y=n,color=group))+
  stat_summary()+
  stat_smooth(method="lm")+
  facet_wrap(.~demo_type)+
  theme_minimal()


```

```{r}
mod_full_data<-social_data%>%group_by(demo_type,player,round,group)%>%
  count(social_info_use)%>%filter(!is.na(social_info_use))%>%filter(social_info_use=="copy")%>%
  brms::brm(n~group*demo_type+round,data=.,family="poisson",chains=4,cores=4)

sjPlot::tab_model(mod_full_data)

plot_model(mod_full_data, type = "pred", terms = c("c12hour", "barthtot [30,50,70]", "c161sex"))

```

#TODO
How much do the copying choices deviate from randomness?

```{r}
mod_gem_found<-social_data%>%group_by(demo_type,player,round,group)%>%
  count(social_info_use)%>%filter(!is.na(social_info_use))%>%filter(demo_type=="gem_found")%>%
  brms::brm(n~group,data=.,family="poisson",chains=4,cores=4)

mod_gem_not_found<-social_data%>%group_by(demo_type,player,round,group)%>%
  count(social_info_use)%>%filter(!is.na(social_info_use))%>%filter(demo_type=="gem_not_found")%>%
  brms::brm(n~group,data=.,family="poisson",chains=4,cores=4)

mod_never_exploit<-social_data%>%group_by(demo_type,player,round,group)%>%
  count(social_info_use)%>%filter(!is.na(social_info_use))%>%filter(demo_type=="never_exploit")%>%
  brms::brm(n~group,data=.,family="poisson",chains=4,cores=4)

mod_no_gem<-social_data%>%group_by(demo_type,player,round,group)%>%
  count(social_info_use)%>%filter(!is.na(social_info_use))%>%filter(demo_type=="no_gem")%>%
  brms::brm(n~group,data=.,family="poisson",chains=4,cores=4)
```
# multilevel model logit?

